---
title: "Solo Project"
execute:
  echo: true
  warning: false
  error: false

format: 
  html: 
    code-fold: true
---

```{r}

library(tidyverse)
library(sf)
library(rnaturalearth)

```



```{r}

covid_in_italy <- read_csv("~/Documents/portfolio-NolanRittenberg/bw/covid19_italy_province.csv")

covid_in_italy_per_region <- covid_in_italy |>
  group_by(RegionName) |>
  summarise(region_cases = n())
  
```

```{r}


italy_shape_file <- read_sf("georef-italy-provincia/georef-italy-provincia-millesime.shp")

italy_map <- ne_states(returnclass = "sf", country = "Italy")

covid_in_italy_per_shape <- italy_shape_file |>
  left_join(covid_in_italy_per_region, join_by(reg_name == RegionName))
  
  
ggplot(covid_in_italy_per_shape) + 
  geom_sf(
    aes(fill = region_cases),
    color = "#f0f0f0",
    size = 0.1
  ) +
  scale_fill_gradient(
    low = "pink",
    high = "darkred",
    name = "Total Number of
COVID-19 Cases"
  ) + 
  labs(title = "Amount of COVID-19 Cases Per Province In Italy (2022)", 
       subtitle = "Grey = N/A", 
       caption = "
       
       By: Nolan Rittenberg | 2025\n
       Source: Italian Civil Protection Department, COVID-19 data repository (https://github.com/pcm-dpc/COVID-19)") + 
  theme_minimal() + 
  theme(
  plot.title = element_text(hjust = 0.3, face = "bold"), 
  plot.subtitle = element_text(hjust = 0.5), 
  plot.caption = element_text(hjust = 0.001, size = 7),
  plot.margin = margin(t = 10, r = 10, b = 20, l = 10)
)

# region_cases are NA for the provinces, Bolzano and Trento. This dataset does not have data for the covid cases in Bolzano and Trento. 

```

In the Year 2022, Italy was hit hard by COVID-19, being at the forefront of Europe's ongoing challenge with COVID-19. The most common areas and provinces for tourism in Italy are very similar to the areas and provinces that had the highest amount of COVID-19 cases. Tourism is a large part of Italy's economy, which makes the implication of COVID-19 regulations particularly challenging. In 2022, Italy understandably decreased their COVID-19 travel regulations however, this led to a serious increase in the number of COVID-19 cases because the most affected areas by COVID-19 were also the most visited areas by tourists. 


























